Crystals

### 2017-05-04 doc/ms.tex
Copy of dnest4 Python stuff, so it's bundled

>>>>

\section{Installation and usage}

\subsection*{Windows}
The entire repository, including C++ and Python source code, and a Windows
executable, is hosted on Bitbucket. The URL for the git repository is

{\tt https://bitbucket.org/eggplantbren/crystals}

If you do not use git, the repository can simply be downloaded from

{\tt https://bitbucket.org/eggplantbren/crystals/get/c78decf570f0.zip}

and unzipped into any location on your computer.
